\Title

### 2020-03-16 manuscript/manuscript.tex
Add flowchart and description of sources comparison

Each source distribution from Table~\ref{tab:source-distributions} needs
certain parameters in order to build the set of point sources.
The prediction capabilities of the source distribution depends on the choice of
these parameters.
For example, locating the sources beneath the data points at constant depth
needs the definition of the \emph{depth} parameter.
If the sources are set too close to the data points, the source distribution
it's very likely to overfit the data: the measured field will be recovered, but
the predictions on unobserved locations will be very inaccurate.
Another parameter that plays an important role on the predictive capabilities
of the sources is the damping parameter.
On real world scenarios, choosing the values of the parameters is a challenging
task: it's not easy to determine the accuracy of the predictions without
knowing the true value of the field on unobserved locations.
This problem can be solved through cross-validation.
When working with a synthetic model, the situation is different: we can compute
the true values of harmonic field generated by the synthetic model on any
point.
Therefore, interpolating the observed data on the same points of the
\emph{target} grid and then scoring the prediction against the true values of
the \emph{target} grid constitutes an objective way to measure the predictive
accuracy of the source distribution.

For each source distribution we proposed different values for each parameter
(including the damping) and combined them into several parameters sets.
For each parameter set we build the sources and fit their coefficients through
least-squares.
Then the sources are used to predict the field on the same points of the
\emph{target} grid and finally we compute the coefficient of determination
(R$^2$ score) between the prediction and the true values of the \emph{target}
grid.
We can therefore obtain the \emph{best prediction} generated by each source
distribution as the one that achieves the highest score.

>>>>

Each source distribution from Table~\ref{tab:source-distributions} needs
certain parameters in order to build the set of point sources.
The prediction capabilities of the source distribution depends on the choice of
these parameters.
For example, locating the sources beneath the data points at constant depth
needs the definition of the \emph{depth} parameter.
If the sources are set too close to the data points, the source distribution
it's very likely to overfit the data: the measured field will be recovered, but
the predictions on unobserved locations will be very inaccurate.
Another parameter that plays an important role on the predictive capabilities
of the sources is the \emph{damping}.

On real world scenarios, choosing the values of the parameters is a challenging
task: it's not easy to determine the accuracy of the predictions without
knowing the true value of the field on unobserved locations.
This problem can be solved through cross-validation.
When working with a synthetic model, the situation is different: we can compute
the true values of harmonic field generated by the synthetic model on any
point.
Therefore, interpolating the observed data on the same points of the
\emph{target} grid and then scoring the prediction against the true values of
the \emph{target} grid constitutes an objective way to measure the predictive
accuracy of the source distribution.

In order to compare the predictive capabilities of each source distribution we
perform a parameter search to obtain the best prediction that can be achieved
by each one of them.
For each source distribution we proposed different values for each parameter
(see Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey}).
These parameters values are combined obtaining several \emph{set of
parameters}.
We use each set of parameters to create the sources, fit their coefficients
through least-squares and predict the field on the same points of the
\emph{target} grid.
We then \emph{score} the prediction by computing the coefficient of
determination (R$^2$ score) between the prediction and the true values of the
\emph{target} grid.
Finally, we obtain the \emph{best prediction} for each source distribution as
the one that achieves the highest score.
See Figure~\ref{fig:flowchart} for a graphical illustration of this process.
This process is carried out on both ground and airborne synthetic surveys.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/flowchart.pdf}
    \caption{
        Flowchart for comparing the performance of the source distributions.
        For each source distribution we propose different values for its
        parameters (see Tables~\ref{tab:parameters-ground-survey}
        and~\ref{tab:parameters-airborne-survey}).
        These values are then combined to obtain several set of parameters
        which are iteratively submitted to the process illustrated on this
        figure.
        Finally we obtain the best prediction generated by each source
        distribution as the one that achieves the best score.
    }
    \label{fig:flowchart}
\end{figure}

Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey} also show the parameter combination
that produces the best prediction for each source distribution and its
corresponding R$^2$ score, for both ground and synthetic surveys, respectively.
Figures~ \ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution, for
both ground and synthetic surveys, respectively.
